---
title: "P8105 Homework5 Solution"
author: "Xun Wang"
date: "11/07/2019"
output: github_document
---

This file is the solution to P8105 Homework 5 from Xun Wang (xw2417).

```{r setup, message=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(10)
```

#### Problem 1

This problem uses the `iris` dataset. The code chunk below loads the dataset and introduces missing values in each column.

```{r}
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

The code chunk below generates a function that takes a vector as an argument; replaces missing values; and returns the resulting vector. 

```{r}
replace_missing = function(x) {
  
  if (is.numeric(x)) {
    x[is.na(x)] = mean(x, na.rm = TRUE)
  } else if (is.character(x)) {
    x[is.na(x)] = "virginica"
  } else {
    stop("Argument x should be numeric or character")
  }
  x
}
```

The code chunk below replaces missing values in the `iris_with_missing` with
* the mean of non-missing values for numeric variables
* "virginica" for character variables
and generates a `tibble` output.

```{r}
iris_complete = map_df(iris_with_missing, replace_missing)

iris_complete
```



